\tool

### 2017-11-28 paper/paper.tex
Adding IBM cite

To make software engineers more effective and efficient in their work, many types of tools have been created to automatically perform code analysis, refactoring, security checks, and more for programmers. One such type is static analysis tools. Static analysis tools can improve software quality by automatically inspecting code without running the program. These tools can be useful for finding code defects early in the development process before code is released. According to a report from IBM, the relative cost for fixing errors also drastically increases the longer the fault exists in the code base through the software development lifecycle. Previous studies also show that static analysis tools are effective in preventing bugs in code to save money for companies in addition to time and effort for developers~\cite{UsingStaticAnalysis}.

>>>>

To make software engineers more effective and efficient in their work, many types of tools have been created to automatically perform code analysis, refactoring, security checks, and more for programmers. One such type is static analysis tools. Static analysis tools can improve software quality by automatically inspecting code without running the program. These tools can be useful for finding code defects early in the development process before code is released. According to a report from IBM, the relative cost for fixing errors also drastically increases the longer the fault exists in the code base through the software development lifecycle~\cite{SoftwareAssuranceSDLC}. Previous studies also show that static analysis tools are effective in preventing bugs in code to save money for companies in addition to time and effort for developers~\cite{UsingStaticAnalysis}.
